Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
more on dep graph
fill in fairly complete book list

Figure~\ref{fig:genealogy} illustrates the relationships between \Hydras packages.

@@

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Software Foundations~\cite{Pierce2007} & 2007 & Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  \end{tabular}
  \caption{Coq book comparison.}
  \label{tbl:loc}
\end{table}

>>>>

Figure~\ref{fig:genealogy} illustrates the relationships between \Hydras packages and show their ancestry from historical Coq contributions.

@@

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Software Foundations~\cite{Pierce2007} & 2007 & Executable\\
  Certified Programming with Dependent Types~\cite{chlipalacpdt2011} & 2011 &  Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  Programs and Proofs~\cite{Sergey:PnP} & 2014 & Executable\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Computer Arithmetic and Formal Proofs~\cite{Boldo2017} & 2017 & Traditional\\
  Mathematical Components~\cite{MCB} & 2018 & Traditional\\
  \hline
  \end{tabular}
  \caption{Coq book comparison.}
  \label{tbl:loc}
\end{table}
